Supplementary material

### 2021-06-25 submission/supplement.rmd
add prediction model of GUSTO-I

>>>>

# Case study
```{r, echo=FALSE, warning=FALSE, message=FALSE}
load(here::here("data/raw/gusto.rda"))
gusto <- gusto %>%
  tibble() %>%
  filter(!is.na(tpa))

gustoTable1 <- gusto %>%
  mutate(
    tpa = factor(
      tpa,
      levels = c(0, 1),
      labels = c(
        "Tissue plasminogen activator",
        "Streptokinase"
      )
    ),
    Age = age,
    Outcome = factor(
      day30,
      levels = c(0, 1),
      labels = c(
        "Alive",
        "Dead"
      )
    )
  )

table1::table1(
  ~ sex + Age + Killip + sysbp + + miloc + pulse + pmi + Outcome | tpa,
  data = gustoTable1
)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
gustoModelData <- gusto %>%
  tibble() %>%
  rename(
    "outcome" = "day30",
    "treatment" = "tpa"
  )

prediction <- rms::lrm(
  outcome ~ treatment + age + Killip + pmin(sysbp, 120) + rms::lsp(pulse, 50) + pmi + miloc,
  data = gustoModelData,
  maxit = 99
)

predictionStats <- rms::val.prob(
  y = gustoModelData$outcome, 
  logit = prediction$linear.predictors,
  logistic.cal = F,
  statloc = FALSE
)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
table <- tibble(
  Metric = c(
    "AUC",
    "Brier score",
    "Emax",
    "E90",
    "Eavg"
  ),
  Value = c(
    predictionStats[2],
    predictionStats["Brier"],
    predictionStats["Emax"],
    predictionStats["E90"],
    predictionStats["Eavg"]
  )
)

 knitr::kable(
    table,
    format      = "latex",
    align       = "r",
    booktabs    = TRUE,
    digits      = 4,
    format.args = list(
      big.mar      = ",",
      decimal.mark = "."
    ),
    caption    = "Evaluation statistics of the prediction model for 30-day mortality in GUSTO-I."
  ) 
```
